\documentclass[twoside]{article}
\usepackage{lmodern}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\addbibresource{sources.bib}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{ulem}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue,
}

\titleformat{\section}[block]{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{0.75em}{0.5em}

\title{Computer Science Report}
\author{Mustafa Ersel Algan \and GH:1030513}
\date{3/10/2024}

\begin{document}
\maketitle{}

\noindent \textbf{Links:} 
\href{https://qwersel.github.io/ersel.github.io/Ersel%20Algan%20CS%20Project/Ersel%20Algan%20HTML%20Portfolio/Computer%20Science%20Portfolio.html}{\underline{\textit{Website}}} 
\textnormal{ and } 
\href{https://github.com/Qwersel/ersel.github.io/tree/4c633d38ef109d9e028325fb7ee654e1b4a1144e/Ersel%20Algan%20CS%20Project}{\underline{\textit{GitHub}}}

\section*{Introduction}
This was my first ever website I created so I tried my best to keep it short and concise. I have included placeholder projects that are subject for change in the future and my contact details on it. For the title of my website, I used a catchy Lobster font to greet the potential employer or reader with something "warm" and then continued in a more professional font, Roboto, to convey the professional tone of my work.

\vspace{1em}

\noindent Additionally, I have created a LaTeX CV to highlight any additional information about me like education and working experience.

\section*{Structure}
\subsection*{Header and Footer}
Header and footer were created mainly for practice and while they were not fully utilized in this work, they still make the website look neater by putting the information in kind of a "box" without cluttering or overstimulating the reader by distracting them from the main information on the website.

\subsection*{Colour Usage}
Various shades of blue were used to keep the web page within a certain colour scheme and not making it too distracting while still providing some variety so that the website does not look unappealing. Blue, white, and black colours give a modern and professional look to the web page.

\section*{Images and Text}
Images do a great job showcasing my work while the correct usage of bold and italics separate content on the page and highlight important information in the text.

\section*{Tools and Technologies Used}
\noindent The website was written entirely in HTML as a learning ground for future projects. I used Notepad++ and then Visual Studio Code for writing the code itself. For some features within the code, I want to highlight the use of links within the text to not clutter the website with robust link strings and the implemented design itself with separating sections of the information into neat frames.

\section*{Conclusion \& Future Improvements}
In conclusion, I believe the strongest suits of my website are simplicity and design choice of putting the information on the page on "different elevations" by the usage of colours and sorting text and images into boxes. 

\vspace{1em}

\noindent In the future, I want to improve the contents inside the footer and heading, work on how to connect several web pages with graphics, create links within images, and specifically this web page could use more structural work by possibly adding more information and expanding on subheadings. Additionally, while the website does work on mobile devices, it looks a bit uneven in certain places. Thus, improvements could be made to make mobile version of the website look neater.

\end{document}
